Chatbots in the classroom: an analysis from the teacher's perspective

### 2021-05-14 edubots_surveys.Rnw
Adds small intro

%%% Begin ...
\begin{document}
\SweaveOpts{concordance=TRUE}

@@

\author[
  addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
  corref={aff1},                       % id of corresponding address, if any
  email={jmerelo@ugr.es}   % email address
]{\inits{J.J.}\fnm{Juan J.} \snm{Merelo}}
\author[
  addressref={aff1},
  email={pacv@ugr.es}   % email address
]{\inits{P.A.}\fnm{Pedro A.} \snm{Castillo}}
\author[
  addressref={aff2},
  email={amorag@ugr.es}
]{\inits{A.M.G}\fnm{Antonio M.} \snm{Mora}}
\author[
  addressref={aff1},
  email={fbarranco@ugr.es}
]{\inits{F.}\fnm{Francisco} \snm{Barranco}}

@@

\begin{keyword}
\kwd{Chatbots}
\kwd{Messaging platforms}
\kwd{Tutorship}
\end{keyword}

@@

% TODO: introduction

@@

>>>>

%%% Begin ...
\begin{document}

@@

\author[
  addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
  corref={aff1},                       % id of corresponding address, if any
  email={jmerelo@ugr.es}   % email address
]{\inits{J.J.}\fnm{Juan J.} \snm{Merelo}}
\author[
  addressref={aff1},
  email={pacv@ugr.es}   % email address
]{\inits{P.A.}\fnm{Pedro A.} \snm{Castillo}}
\author[
  addressref={aff2},
  email={amorag@ugr.es}
]{\inits{A.M.G}\fnm{Antonio M.} \snm{Mora}}
\author[
  addressref={aff1},
  email={fbarranco@ugr.es}
]{\inits{F.}\fnm{Francisco} \snm{Barranco}}<

@@

\begin{keyword}
\kwd{Chatbots}
\kwd{Messaging platforms}
\kwd{Tutorship}
\kwd{Educational bots}
\kwd{Higher education}
\end{keyword}

@@

% TODO: introduction
Introduction of new technologies in the classroom needs a combination of teacher education, as well as student willingness and skills. Some technologies are readily adapted, some of them take a long time to be adopted. In most cases, success or failure of the introduction of a

@@

\section{Conclusions}

\section*{Acknowledgements}
